Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2020-06-18 paper/introduction.tex
decrease table row spacing
Minor changes

In this work, we develop an empirical surrogate model for the tritium breeding
ratio (TBR) in an inertial confinement fusion (ICF) reactor. The
expensive model which our surrogate model approximates is a Monte Carlo (MC)
neutronics simulation, \textit{Paramak} (provided by collaborator
Jonathan Shimwell at UKAEA) which returns a prediction of the TBR for a given configuration of a spherical ICF reactor.

@@

    \caption{Diagram of the simple sphere geometry (not to scale) where the blanket is \fcolorbox{white}{green}{\rule{0pt}{6pt}\rule{6pt}{0pt}}, the firstwall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.}
    \label{fig:model_diagram}
\end{figure}

@@

\begin{table}[t]
	\setlength\tabcolsep{2pt}
	\caption{\label{tbl:params}Input parameters supplied to the MC TBR simulation in alphabetical
		order. Groups of fractions marked\textsuperscript{\textdagger
		\textdaggerdbl} are independently required to sum to 1.}
	\begin{indented}
	\item[]
		\begin{tabular}{l|ll}
		\toprule
		{} & Parameter name & Domain\\
		\midrule
		\parbox[t]{2mm}{\hspace{-2pt}\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
		   & Breeder fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Breeder \isotope[6]{Li} enrichment fraction & $[0,1]$\\
		   & Breeder material & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
		   & Breeder packing fraction & $[0,1]$\\
		   & Coolant fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
		   & Multiplier fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Multiplier material & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
		   & Multiplier packing fraction & $[0,1]$\\
		   & Structural fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
		   & Thickness & $[0,500]$\\
		\midrule
		\parbox[t]{2mm}{\hspace{-2pt}\multirow{6}{*}{\rotatebox[origin=c]{90}{First wall}}}
		   & Armour fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Coolant fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
		   & Structural fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
		   & Thickness & $[0,20]$\\
		\bottomrule
		\end{tabular}
	\end{indented}
\end{table}

>>>>

In this work, we develop an empirical
surrogate model for the tritium breeding ratio
(TBR) in an inertial confinement fusion (ICF)
reactor. The expensive model which our
surrogate model approximates is a Monte
Carlo (MC) neutronics simulation, \textit{Paramak} which returns a prediction of the TBR for a given configuration of a spherical
ICF reactor. This was achieved by containerizing (using Docker) the neutronics workflow and providing a (python flask based) API interface that returned TBR values for the provided inputs. The neutronics workflow used OpenMC, Fendl 3.1d nuclear data and a Python 3 environment for receiving the API inputs and for driving the model creation, simulation and results extraction.

@@

    \caption{Diagram of the simple sphere geometry (not to scale) where the blanket is \fcolorbox{white}{green}{\rule{0pt}{6pt}\rule{6pt}{0pt}}, the first wall is \fcolorbox{white}{blue}{\rule{0pt}{6pt}\rule{6pt}{0pt}} and the neutron point source is \fcolorbox{white}{red}{\rule{0pt}{6pt}\rule{6pt}{0pt}}.}
    \label{fig:model_diagram}
\end{figure}

@@

\begin{table}[t]
	\setlength\tabcolsep{2pt}
	\renewcommand{\arraystretch}{0.95}
	\caption{\label{tbl:params}Input parameters supplied to the MC TBR simulation in alphabetical
		order. Groups of fractions marked\textsuperscript{\textdagger
		\textdaggerdbl} are independently required to sum to 1.}
	\begin{indented}
	\item[]
		\begin{tabular}{l|ll}
		\toprule
		{} & Parameter name & Domain\\
		\midrule
		\parbox[t]{2mm}{\hspace{-2pt}\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
		   & Breeder fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Breeder \isotope[6]{Li} enrichment fraction & $[0,1]$\\
		   & Breeder material & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
		   & Breeder packing fraction & $[0,1]$\\
		   & Coolant fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
		   & Multiplier fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Multiplier material & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
		   & Multiplier packing fraction & $[0,1]$\\
		   & Structural fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
		   & Thickness & $[0,500]$\\
		\midrule
		\parbox[t]{2mm}{\hspace{-2pt}\multirow{6}{*}{\rotatebox[origin=c]{90}{First wall}}}
		   & Armour fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Coolant fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
		   & Structural fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
		   & Thickness & $[0,20]$\\
		\bottomrule
		\end{tabular}
	\end{indented}
\end{table}

### 2020-06-18 paper/methodology.tex
Minor changes

The objective of Experiment~1 is to simplify the regression task for
surrogates prone to suboptimal performance in discontinuous spaces.
To this end, training points are filtered to a single selected discrete feature
assignment, and surrogates are trained only on the remaining continuous features.
This is repeated several times to explore variances in behaviour,
particularly in 4~distinct assignments that are obtained by setting blanket and
firstwall coolant materials to one
of:~$\{\text{H\textsubscript{2}O},\isotope{He}\}$.
Experiment~2 conventionally measures surrogate performance on the full feature
space without any parameter restrictions. In both experiments, hyperparameter tuning is
facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We select the
hyperparameter configuration that produces the model that maximises $R^2$. The
process is terminated after 1000~iterations or 2~days, whichever condition is satisfied first.
The results of Experiments~1 \&~2 are depicted
in Figures~\ref{fig:exp1-time-vs-reg} \&~\ref{fig:exp2-time-vs-reg}
respectively, and described in~\Sref{sec:res-exp12}.

>>>>

The objective of Experiment~1 is to simplify the regression task for
surrogates prone to suboptimal performance in discontinuous spaces.
To this end, training points are filtered to a single selected discrete feature
assignment, and surrogates are trained only on the remaining continuous features.
This is repeated several times to explore variances in behaviour,
particularly in 4~distinct assignments that are obtained by setting blanket and
first wall coolant materials to one
of:~$\{\text{H\textsubscript{2}O},\isotope{He}\}$.
Experiment~2 conventionally measures surrogate performance on the full feature
space without any parameter restrictions. In both experiments, hyperparameter tuning is
facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We select the
hyperparameter configuration that produces the model that maximises $R^2$. The
process is terminated after 1000~iterations or 2~days, whichever condition is satisfied first.
The results of Experiments~1 \&~2 are depicted
in Figures~\ref{fig:exp1-time-vs-reg} \&~\ref{fig:exp2-time-vs-reg}
respectively, and described in~\Sref{sec:res-exp12}.
